\documentclass[tocstyle=ref-genre]{ees}

\shorttitle{Opus patheticum}

\begin{document}

\eesTitlePage

\eesCriticalReport{
  – & – & – & Grace notes are generally written out in \B2. \\
    & – & vl & Inconsistent articulation has been tacitly emended. \\
    & – & org & Bass figures are missing throughout \B2. \\
  \midrule
  1 & 15 & org & 1st \eighthNote\ in \B2: d8 \\
    & 26 & org & 1st \eighthNote\ in \B1 and \B2: \flat e8 \\
    & 65 & vla & bar in \B2: 16 × d′16 \\
  \midrule
  2 & 50 & org & 4th to 6th \eighthNote\ in \B2: \flat e8–d8–c8 \\
    & 75 & org & bar in \B1: \flat e2–\crotchetRest \\
    & 79 & org & bar in \B1: \flat b4–\flat B4–\crotchetRest \\
    & 88 & org & 2nd \quarterNote\ in \B1 and \B2: \crotchetRest \\
  \midrule
  4 & 5 & vl 2 & last \eighthNote\ in \B1: g′8 \\
    & 9–16 & vla & bars missing in \B1 \\
    & 40 & vla & 3rd \quarterNote\ in \B1 and \B2: \flat a4 \\
    & 40–41 & org & bass figures missing in \B1 \\
    & 85 & vl 1 & 2nd/3rd \eighthNote\ in \B1: f″8–g″16–f″16 \\
    & 102 & org & bar in \B2 one octave higher \\
  \midrule
  5 & – & – & This edition replicates the movement from \B1. In this source, bars 159–203 are indicated by the directive “Ritornello da capo al segno fine” (or similar) in vl 1, vl 2, vla, vlne, and org; B contains a multimeasure rest comprising 44 bars. Hence, bars 159–203 correspond to bars 1–45. \B2 differs in two respects from \B1. First, the da capo is shorter, since it only comprises bars 8–11, 31–40, and 45 (segno bar between bars 7 and 8; “vi – de” indications in red pencils, skipping bars 12–30 and 41–44). Second, bars 59–64 and 119–121 are written in f minor and \flat e minor, respectively (here indicated by parenthesized signs). \B3 differs from \B1 in the following respects: (1) The introduction as well as the da capo omit bars 12–30 and 41–44. (2) Bars 59–64 and 119–121 appear in minor keys (like in \B2). (3) The lyrics are the same as in the first movement (i.\,e., “Septem tuos dolores …). Accordingly, minor differences appear in the B notes. Here, the lower B staff corresponds to the B part of B3. (4) There are minor differences regarding articulation in all instruments. \\
    & 29 & vl 1 & 3rd \quarterNote\ in \B1: g″8–f″8 \\
    & 85 & B & grace note missing in \B1 and \B2 \\
    & 129 & vl 2 & 3rd \quarterNote\ in \B1: \flat e′4 \\
    & 132 & vl 2 & bar in \B1 and \B2: d′2. \\
    & 187 & vl 1 & see bar 29 \\

}

\eesToc{
  \begin{movement}{septem}
    \voice[Coro]
    Septem tuos dolores,\\
    Maria, dum considero,\\
    tecum pati labores,\\
    tecum mori desidero.
  \end{movement}

  \begin{movement}{annae}
    \voice[Tenore]
    Annae gemit senectus,
    et Simeon affligitur,
    doloris ense pectus,
    quando tibi transfigitur.
  \end{movement}

  \begin{movement}{aegyptus}
    \voice[Alto]
    Aegyptus est asyli
    lucus tuis amoribus,
    iuxta fluenta Nyli
    liquescis in doloribus.
  \end{movement}

  \begin{movement}{inpatris}
    \voice[Basso]
    In Patris esse rebus
    cum nesciebas Filium
    visa es tribus diebus
    pallere sicut lilium.
  \end{movement}

}

\eesScore

\end{document}
